Title

### 2023-06-02 main.tex
Reset error count between rows. herpderp

We have discussed the main features of quantum channels and 
now we turn our attention to a specific 
type of channels for $N$-qubit systems called Pauli channels.
First we will define these channels for single-qubit systems,
whose most general density matrix can be written as~\cite{chuangbook}:
\begin{equation}
\label{eq: Density Matrix}
\rho = \dfrac{1}{2} \sum_{\alpha=0}^{3} r_{\alpha} \sigma_{\alpha},
\end{equation}
with $\sigma_0 = \mathbb{I}$, and $\sigma_{1,2,3}$ the usual Pauli matrices.
The condition $\tr(\rho) = 1$ requires that $r_0 = 1$ while $\rho \geq 0$ 
implies that the remaining $r_{1,2,3}$ form
a vector $\vec{r}= (r_1,r_2,r_3)$ inside a unit sphere known as the Bloch sphere~\cite{Marinescu}.
That is, every possible density matrix for a one-qubit
system is uniquely associated with a point in a unit sphere. 
% \cpnote{explicar un poco mejor. Me parece que para el publico vale 
% la pena ser un poco mas explicito. pero no estoy muy seguro.}

@@

In this section we propose a quantum circuit that simulates $N$-qubit Pauli
channels.  Moreover, we implement the circuit for $N=1$ on a quantum computer
and analyze the results using the diamond norm.
We find that close to the depolarizing channel, the general circuit simulator 
can implement such channels with the highest fidelity. 
% produce the highest 
% \cpnote{Quizá en una frase poner el resultado aca o ampliar
% tantito} \tbnote{Va, agregué lo siguiente: 
% We conclude that the circuit performs optimally for channels  in proximity to the
% completely depolarizing channel but
% it is deficient close to unitary channels.}
% }}} 
\subsection{Description of the Circuit for a Pauli Channel} %{{{
\label{subsec: Description of the circuit}

% \cpnote{Yo abriría este parrafo con una frase que de la idea muy general. Decir 
% algo asi como que vamos a crear un estado conque contenga a las $k$s 
% como coeficientes y leugo controlar la aplicación de los Pauli strings. Luego
% ya dar los detalles. Así incluso mas escueto de lo que pongo. Por ejemplo:
% To design the circiot that implements 13, we construct a state that incorportes
% probabilities $k$ and subsequently apply controlled operation. In particular... }
% \cpnote{No me gusta como está organizado este parrafo. Le puedes dar una iterada?}
% \tbnote{Propongo el párrafo en naranja para sustituirlo}

@@

The first part of the circuit involves the creation of the state
\begin{eqnarray}
\label{eq: state}
\text{Ancilla state =} 
\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
\end{eqnarray}
on the ancilla qubits, where $b_{\vec{\gamma}}$ are numbers such that $
|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$ and
the $2N$-qubit state $|\vec{\gamma}\rangle$ is defined as $|\gamma_1\rangle
\cdots |\gamma_N\rangle$.
% \cpnote{La primera frase es cierta, pero no le veo el sentido acá. Trata de reformular el parrafo 
% de nuevo. Croe que el ``This means'' definitivamente no va y es el que le da un sentido ``raro''. 
% Itera (quizá solo quitando esas dos palabras)} \tbnote{Concuerdo, quité eso.}
When measured in the computational basis, the state given in \eref{eq: state}
collapses to $|\vec{\gamma}\rangle$ with a 
probability $|b_{\vec{\gamma}}|^2 = k_{\vec\gamma}$. 
The circuit in \fref{fig: circuit-pauli} uses this fact
to apply $\sigma_{\vec{\gamma}}$ on the main qubits
with a probability $k_{\vec\gamma}$ by using controlled operations 
conditioned on the state of the system being $|\vec{\gamma}\rangle$,
just as the Pauli channel is supposed to do.  
% 
% that apply $\sigma_{\vec{\gamma}}$ to the main qubits
% only if the ancilla qubits are in the state $|\vec{\gamma}\rangle$.
% 
% Therefore, the circuit from \fref{fig: circuit-pauli} 
% applies each operation $\sigma_{\vec{\gamma}}$ to the principal qubits 
% with a probability $k_{\vec{\gamma}}$, 
% just as a Pauli channel is supposed to do.

@@

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in \fref{fig: circuit-pauli-1},
which is a special case of \fref{fig: circuit-pauli}
but with all details  explicitly shown.
In said figure, the ancilla state
of \eref{eq: state} can be taken to be
$\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
|10\rangle + \sqrt{k_{11}}|11\rangle$
and it is created on the ancilla qubits with the help of three rotations of angles:
\begin{subequations}
\begin{eqnarray}
\theta_0 &= &\arctan(\sqrt{k_{01}/k_{00}}) -
\arctan(\sqrt{k_{11}/k_{10}}),
\label{eq:angle1} \\ 
\theta_1 &= &2 \arccos(\sqrt{k_{00} +
k_{01}}),
\label{eq:angle2} \\
\theta_2 &= &\arctan(\sqrt{k_{01}/k_{00}}) +
\arctan(\sqrt{k_{11}/k_{10}}).
\label{eq:angle3}
\end{eqnarray}
\label{eq:angle}
\end{subequations}
\cpnote{Quisiera ver las ecuaciones sin la teheta despejada. Por ejemplo la de theta 1
es $\cos^2 (\theta_1/2) = k00 + k01$ bueno mas bonita, pero asi. Luego las de tehta0 y theta2 
quizá tambien sean sencillas. Las quiero ver!!!}
\tbnote{Ah, ya entiendo. Las única forma que veo de escribirlas es:
\begin{align*}
\tan \theta_0 = \dfrac{\sqrt{k_{01}/k_{00}} - \sqrt{k_{11}/k_{10}}}{1+\sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}}}} \\
\tan \theta_2 = \dfrac{\sqrt{k_{01}/k_{00}} + \sqrt{k_{11}/k_{10}}}{1-\sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}}}}
\end{align*}
No veo cómo escribir ecuaciones de las thetas no despejadas que sean sencillas.
}

\begin{figure} % {{{
\centering
\includegraphics{images/circuito_unqubit.pdf}
\caption{
% \cpnote{ No me gusta que esté tan cargado de ecuaciones el caption. Metelas en
% el lugar apropiado en el texto} \tbnote{Lo pasé al texto}
{\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
which is a particular case of \fref{fig: circuit-pauli}.  Here we have two
ancilla qubits and we use three rotations
of angles given by \eref{eq:angle} to create the Ancilla State of
of \eref{eq: state} for the two ancilla qubits.
\cpnote{Creo qeu este seria el estado ecuacion 14, pero como qeuno está limpio. 
Creo quepodemos nombrar ese estado y luego referirnos acá por el nobmre y la referencia 
a la ecuación.} \tbnote{Ya}
}
\label{fig: circuit-pauli-1} 
\end{figure} % }}}

@@

% \cpnote{Toca rediseñar este parrafo mejor. La figura que al final nos interesa
% es la $f$, pero no se menciona acá. Toca como que hacer que el párrafo gire
% alrededor de ella. }

% \tbnote{Rediseño párrafo anterior: }
% {\color{orange}  
We took a sample of one-qubit Pauli channels
and evaluated their implementation on IBM's
ibmq-lima quantum computer~\cite{Qiskit},
as shown in \fref{fig:fids}. 
For each of the channels sampled, we used 
quantum process tomography~\cite{Qiskit, Chuang:1996} to obtain the 
operator $\xi_I$ corresponding to the implementation of the
circuit in the quantum computer. 
Then, we compared $\xi_I$ with the theoretical 
operator $\xi_T$ of the Pauli channel we wanted to implement.
To see how close the operators $\xi_I$ and 
$\xi_T$ are, we shall use the
diamond distance~\cite{Aharonov,Wilde}, which is defined by
\begin{equation}
||\xi_I - \xi_T ||_{\diamond}  = \max_{\rho} || (\xi_I \otimes I) \rho - (\xi_T \otimes I) \rho ||_1,
\end{equation}
with $I$ the identity map,
$|| \cdot ||_1$ the trace norm and the maximization
done over all density matrices $\rho$.
The calculation of this norm is done using the semi-definite program from reference \cite{Watrous}.
When the two channels are the same,
the diamond distance has a value of $0$, while in the case that the channels
are completely distingushable, the distance reaches its maximum value of $2$~\cite{Benenti}.
For the analysis done in \fref{fig:fids}, we define a sort of ``diamond fidelity'' as: 
\begin{equation}
f = 1 - \dfrac{1}{2} ||\varepsilon_I - \varepsilon_T ||_{\diamond},
\label{eq:diamond-fid}
\end{equation}
which ranges from $0$, when the channels have a maximum distance, to  $1$,
when they are exactly equal.

% \cpnote{hummm ejemplo al menos para nosotros.} 
% \tbnote{Un ejemplo que comprobé es considerar el canal que aplica $\sigma_x$ y 
% el que aplica $\sigma_z$ y tienen $p_{\succ}=1$.
% De hecho, al tomar dos canales que consistan en aplicar $\sigma_i$ y $\sigma_j$ 
% (para $i\neq j$), se cumple esto.
% También quería ejemplos no unitarios, pero no encontré.}

@@

\begin{theorem}
Consider a 1PR circuit of $N$ qubits
and denote by $U$ the operator it implements on this system. 
Then, for every $j \in \{0, 1, \cdots, 2^N-1\}$, 
we have that:
\begin{align*}
U|j\rangle = e^{is} |a^j\rangle + e^{-is} |b^j\rangle + |c^j\rangle
\end{align*}
with $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states and $|a^j|^2 + |b^j|^2 + |c^j|^2 = 1$.
\end{theorem}
\textbf{Proof:} 
\cpnote{Sugiero cambiar la a gargoleada por una a con gorro o con tilde. No se 
usa asi cambiar de fuente.} \tbnote{Va, listo}
We can conclude from theorem 1 that $U=ARB$,
where $A$ and $B$ are unitary matrices and $R$ is a $\sigma_3$ rotation of angle $2s$
applied to the last qubit and controlled by some of the other ones.

@@

\cpnote{Separo el parrafo par auqe cada matriz tenga como su propio espacio.} \tbnote{Va, excelente.}
Then, the rotation $R$ will only affect the states on the first sum (since they fulfill the control conditions)
and not the others. Therefore,  
remembering that a $\sigma_3$ rotation acts by adding a phase $e^{-is}$ to $|0\rangle$
and a phase $e^{is}$ to $|1\rangle$, we have that,
% \begin{small}
% \begin{eqnarray}
% &e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle 
% + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
% & \qquad = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
% \end{eqnarray}
% \end{small}
% test
\begin{align}
RB|j\rangle& = e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1\rangle 
+ \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right) \nonumber \\
& = e^{-is} |\tilde{b}^{j}\rangle + e^{is} |\tilde{a}^j\rangle + |\tilde{c}^j\rangle
\end{align}
where we defined
\begin{align*}
|\tilde{a}^j \rangle &= \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle,\\
|\tilde{b}^j\rangle &= \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |0 \rangle,\\
|\tilde{c}^j\rangle &= \sum_{k \not\in \mathcal{C}}\left( B_{2k,j} |k\rangle|0\rangle+ B_{2k+1,j} |k \rangle |1\rangle  \right).
\end{align*}
\cpnote{Acá puedes usar align. Creo que es mucho para dejarlas en el texto. Recuerda la puntuacion. 
Me está gustando mucho la explicacion. Simple y clara. }
\tbnote{Listo.}
These states are clearly orthogonal because they are each linear combinations of different 
orthogonal states of the computational basis. 
Moreover, they satisfy  $|\tilde{a}^j|^2 + |\tilde{b}^j|^2 + |\tilde{c}^j|^2 = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
which is unitary.

@@

\cpnote{Acá voy}

This theorem implies that starting from the state $|0\rangle$ (or any 
other starting state),
the only curves of states we could expect to create
with a 1PR circuit are those of the form $U|0\rangle$, that is, curves such as:
\begin{equation}
|\eta(p)\rangle = |c\rangle + e^{is}|a\rangle + e^{-is} |b\rangle,
\label{eq:curve-states}
\end{equation}
with 
\begin{equation}
|a|^2 + |b|^2 + |c|^2 = 1  \; \text{and} \; |a\rangle, |b\rangle, |c\rangle \; \text{orthogonal states},
\label{eq:conditions-vecs}
\end{equation}
and $s = s(p)$ a function of $p$.
Furthermore, given a curve of states as the one in
\eref{eq:curve-states}, we can always construct a 1PR circuit to create it.
One way of doing it, is to use the circuit of \fref{fig:1PR-circuit}, setting the parametrized
rotation $R$ on the last qubit to be controlled by all the other qubits
and defining the operators $A$ and $B$ by:
\begin{align*}
&B|0\rangle = |a| |2^{N}-1 \rangle + |b| |2^{N}-2\rangle + |c| |2^N-3\rangle, \\
&A|2^N-1 \rangle = \frac{1}{|a|} |a\rangle,\; A|2^{N}-2\rangle = \frac{1}{|b|}|b\rangle, \; A|2^{N}-3\rangle = \frac{1}{|c|}|c\rangle.
\end{align*}
The rest of the operators $A$ and $B$ can be
defined arbitrarily in any way such that they are unitary.
Then, starting from the initial state $|0\rangle$
and applying the circuit  of \fref{fig:1PR-circuit}, 
some direct calculations lead us  to 
the resulting curve of states
of \eref{eq:curve-states}.
To see it, notice that rewriting the expression of  $B|0\rangle$ by separating the
first $N-1$ qubits from the last one,
we have that $$B|0\rangle = |a| |2^{N-1}-1\rangle |1\rangle + |b| |2^{N-1}-1\rangle |0\rangle + |c| |2^{N-1}-2\rangle |1\rangle.$$
Then, since the parametrized rotation $R$ is controlled by all the first $N-1$ qubits, it only applies
to the first two terms of $B|0\rangle$ 
and gives as a result
$$
RB|0\rangle =|a| e^{is} |2^{N-1}-1\rangle |1\rangle + |b| e^{-is} |2^{N-1}-1\rangle |0\rangle + |c| |2^{N-1}-2\rangle |1\rangle.
$$
Finally, applying $A$ as defined above to this state leads to the desired result.

@@

\section{Conclusion} % {{{
\tbnote{Poner luego}
% }}}
\section{Supporting information} % {{{

>>>>

We have discussed the main features of quantum channels and 
now we turn our attention to a specific 
type of channels for $N$-qubit systems called Pauli channels.
First we will define these channels for single-qubit systems,
whose most general density matrix can be written as~\cite{chuangbook}:
\begin{equation}
\label{eq: Density Matrix}
\rho = \dfrac{1}{2} \sum_{\alpha=0}^{3} r_{\alpha} \sigma_{\alpha},
\end{equation}
with $\sigma_0 = \mathbb{I}$, and $\sigma_{1,2,3}$ the usual Pauli matrices.
The condition $\tr(\rho) = 1$ requires that $r_0 = 1$ while $\rho \geq 0$ 
implies that the remaining $r_{1,2,3}$ form
a vector $\vec{r}= (r_1,r_2,r_3)$ inside a unit sphere known as the Bloch sphere~\cite{Marinescu}.
That is, every possible density matrix for a one-qubit
system is uniquely associated with a point in a unit sphere.

@@

In this section we propose a quantum circuit that simulates $N$-qubit Pauli
channels.  Moreover, we implement the circuit for $N=1$ on a quantum computer
and analyze the results using the diamond norm.
We find that close to the depolarizing channel, the general circuit simulator 
can implement such channels with the highest fidelity. 
% produce the highest 
% }}} 
\subsection{Description of the Circuit for a Pauli Channel} %{{{
\label{subsec: Description of the circuit}

@@

The first part of the circuit involves the creation of the state
\begin{eqnarray}
\label{eq: state}
\text{Ancilla state =} 
\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
\end{eqnarray}
on the ancilla qubits, where $b_{\vec{\gamma}}$ are numbers such that $
|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$ and
the $2N$-qubit state $|\vec{\gamma}\rangle$ is defined as $|\gamma_1\rangle
\cdots |\gamma_N\rangle$.
When measured in the computational basis, the state given in \eref{eq: state}
collapses to $|\vec{\gamma}\rangle$ with a 
probability $|b_{\vec{\gamma}}|^2 = k_{\vec\gamma}$. 
The circuit in \fref{fig: circuit-pauli} uses this fact
to apply $\sigma_{\vec{\gamma}}$ on the main qubits
with a probability $k_{\vec\gamma}$ by using controlled operations 
conditioned on the state of the system being $|\vec{\gamma}\rangle$,
just as the Pauli channel is supposed to do.  
% 
% that apply $\sigma_{\vec{\gamma}}$ to the main qubits
% only if the ancilla qubits are in the state $|\vec{\gamma}\rangle$.
% 
% Therefore, the circuit from \fref{fig: circuit-pauli} 
% applies each operation $\sigma_{\vec{\gamma}}$ to the principal qubits 
% with a probability $k_{\vec{\gamma}}$, 
% just as a Pauli channel is supposed to do.

@@

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in \fref{fig: circuit-pauli-1},
which is a special case of \fref{fig: circuit-pauli}
but with all details  explicitly shown.
In said figure, the ancilla state
of \eref{eq: state} can be taken to be
$\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
|10\rangle + \sqrt{k_{11}}|11\rangle$
and it is created on the ancilla qubits with the help of three rotations of angles:
\begin{subequations}
\begin{eqnarray}
\theta_0 &= &\arctan(\sqrt{k_{01}/k_{00}}) -
\arctan(\sqrt{k_{11}/k_{10}}),
\label{eq:angle1} \\ 
\theta_1 &= &2 \arccos(\sqrt{k_{00} +
k_{01}}),
\label{eq:angle2} \\
\theta_2 &= &\arctan(\sqrt{k_{01}/k_{00}}) +
\arctan(\sqrt{k_{11}/k_{10}}).
\label{eq:angle3}
\end{eqnarray}
\label{eq:angle}
\end{subequations}
\cpnote{Quisiera ver las ecuaciones sin la teheta despejada. Por ejemplo la de theta 1
es $\cos^2 (\theta_1/2) = k00 + k01$ bueno mas bonita, pero asi. Luego las de tehta0 y theta2 
quizá tambien sean sencillas. Las quiero ver!!!}
\tbnote{Ah, ya entiendo. Las única forma que veo de escribirlas es:
\begin{align*}
\tan \theta_0 = \dfrac{\sqrt{k_{01}/k_{00}} - \sqrt{k_{11}/k_{10} }}{1+\sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}} }} \\
\tan \theta_2 = \dfrac{\sqrt{k_{01}/k_{00}} + \sqrt{k_{11}/k_{10} }}{1-\sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}} }}
\end{align*}
No veo cómo escribir ecuaciones de las thetas no despejadas que sean sencillas.
}

\begin{figure} % {{{
\centering
\includegraphics{images/circuito_unqubit.pdf}
\caption{
{\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
which is a particular case of \fref{fig: circuit-pauli}.  Here we have two
ancilla qubits and we use three rotations
of angles given by \eref{eq:angle} to create the Ancilla State of
of \eref{eq: state} for the two ancilla qubits.
}
\label{fig: circuit-pauli-1} 
\end{figure} % }}}

@@

We took a sample of one-qubit Pauli channels
and evaluated their implementation on IBM's
ibmq-lima quantum computer~\cite{Qiskit},
as shown in \fref{fig:fids}. 
For each of the channels sampled, we used 
quantum process tomography~\cite{Qiskit, Chuang:1996} to obtain the 
operator $\xi_I$ corresponding to the implementation of the
circuit in the quantum computer. 
Then, we compared $\xi_I$ with the theoretical 
operator $\xi_T$ of the Pauli channel we wanted to implement.
To see how close the operators $\xi_I$ and 
$\xi_T$ are, we shall use the
diamond distance~\cite{Aharonov,Wilde}, which is defined by
\begin{equation}
||\xi_I - \xi_T ||_{\diamond}  = \max_{\rho} || (\xi_I \otimes I) \rho - (\xi_T \otimes I) \rho ||_1,
\end{equation}
with $I$ the identity map,
$|| \cdot ||_1$ the trace norm and the maximization
done over all density matrices $\rho$.
The calculation of this norm is done using the semi-definite program from reference \cite{Watrous}.
When the two channels are the same,
the diamond distance has a value of $0$, while in the case that the channels
are completely distingushable, the distance reaches its maximum value of $2$~\cite{Benenti}.
For the analysis done in \fref{fig:fids}, we define a sort of ``diamond fidelity'' as: 
\begin{equation}
f = 1 - \dfrac{1}{2} ||\varepsilon_I - \varepsilon_T ||_{\diamond},
\label{eq:diamond-fid}
\end{equation}
which ranges from $0$, when the channels have a maximum distance, to  $1$,
when they are exactly equal.

@@

\begin{theorem}
Consider a 1PR circuit of $N$ qubits
and denote by $U$ the operator it implements on this system. 
Then, for every $j \in \{0, 1, \cdots, 2^N-1\}$, 
we have that:
\begin{align*}
U|j\rangle = e^{is} |a^j\rangle + e^{-is} |b^j\rangle + |c^j\rangle
\end{align*}
with $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states and $|a^j|^2 + |b^j|^2 + |c^j|^2 = 1$.
\end{theorem}
\textbf{Proof:} 
We can conclude from theorem 1 that $U=ARB$,
where $A$ and $B$ are unitary matrices and $R$ is a $\sigma_3$ rotation of angle $2s$
applied to the last qubit and controlled by some of the other ones.

@@

Then, the rotation $R$ will only affect the states on the first sum (since they fulfill the control conditions)
and not the others. Therefore,  
remembering that a $\sigma_3$ rotation acts by adding a phase $e^{-is}$ to $|0\rangle$
and a phase $e^{is}$ to $|1\rangle$, we have that,
% \begin{small}
% \begin{eqnarray}
% &e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle 
% + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
% & \qquad = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
% \end{eqnarray}
% \end{small}
% test
\begin{align}
RB|j\rangle& = e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1\rangle 
+ \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right) \nonumber \\
& = e^{-is} |\tilde{b}^{j}\rangle + e^{is} |\tilde{a}^j\rangle + |\tilde{c}^j\rangle
\end{align}
where we defined
\begin{align*}
|\tilde{a}^j \rangle &= \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle,\\
|\tilde{b}^j\rangle &= \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |0 \rangle,\\
|\tilde{c}^j\rangle &= \sum_{k \not\in \mathcal{C}}\left( B_{2k,j} |k\rangle|0\rangle+ B_{2k+1,j} |k \rangle |1\rangle  \right).
\end{align*}
These states are clearly orthogonal because they are each linear combinations of different 
orthogonal states of the computational basis. 
Moreover, they satisfy  $|\tilde{a}^j|^2 + |\tilde{b}^j|^2 + |\tilde{c}^j|^2 = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
which is unitary.

@@

This theorem implies that starting from the state $|0\rangle$ (or any 
other state),
the only curves of states we could expect to create
with a 1PR circuit are those of the form 
\begin{equation}
|\eta(p)\rangle = |c\rangle + e^{is}|a\rangle + e^{-is} |b\rangle,
\label{eq:curve-states}
\end{equation}
with 
\begin{equation}
|a|^2 + |b|^2 + |c|^2 = 1,  \quad
\langle a |b\rangle =
\langle a |c\rangle =
\langle b |c\rangle = 0
% , |b\rangle, |c\rangle \; \text{orthogonal states},
%  \text{and} \; |a\rangle, |b\rangle, |c\rangle \; \text{orthogonal states},
\label{eq:conditions-vecs}
\end{equation}
and $s = s(p)$ a function of $p$.
\cpnote{Es un poco confusa la notacion. Hablas de la norma de a con $|a|$, pero ahi parece
que $a$ es un vector. Sugiero cambiar a $\langle a | a \rangle$ o algo asi sin cargar mucho
la notacion. }
\cpnote{Tambien siento qeu las palabras son un poco raras. Sugiero pasarlo por Chatgpt y 
luego tunearlo (todo este parrafo). Avisame cuando quede eso!}
Furthermore, given a curve of states as the one in
\eref{eq:curve-states}, we can always construct a 1PR circuit to create it.
One way of doing it, is to use the circuit of \fref{fig:1PR-circuit}, setting the parametrized
rotation $R$ on the last qubit to be controlled by all the other qubits
and defining the operators $A$ and $B$ by:
\begin{align*}
&B|0\rangle = |a| |2^{N}-1 \rangle + |b| |2^{N}-2\rangle + |c| |2^N-3\rangle, \\
&A|2^N-1 \rangle = \frac{1}{|a|} |a\rangle,\; A|2^{N}-2\rangle = \frac{1}{|b|}|b\rangle, \; A|2^{N}-3\rangle = \frac{1}{|c|}|c\rangle.
\end{align*}
The rest of the operators $A$ and $B$ can be
defined arbitrarily in any way such that they are unitary.
Then, starting from the initial state $|0\rangle$
and applying the circuit  of \fref{fig:1PR-circuit}, 
some direct calculations lead us  to 
the resulting curve of states
of \eref{eq:curve-states}.
To see it, notice that rewriting the expression of  $B|0\rangle$ by separating the
first $N-1$ qubits from the last one,
we have that $$B|0\rangle = |a| |2^{N-1}-1\rangle |1\rangle + |b| |2^{N-1}-1\rangle |0\rangle + |c| |2^{N-1}-2\rangle |1\rangle.$$
Then, since the parametrized rotation $R$ is controlled by all the first $N-1$ qubits, it only applies
to the first two terms of $B|0\rangle$ 
and gives as a result
$$
RB|0\rangle =|a| e^{is} |2^{N-1}-1\rangle |1\rangle + |b| e^{-is} |2^{N-1}-1\rangle |0\rangle + |c| |2^{N-1}-2\rangle |1\rangle.
$$
Finally, applying $A$ as defined above to this state leads to the desired result.

@@

% }}}
\section{Conclusion} % {{{
\tbnote{Poner luego}
% }}}
\section{Supporting information} % {{{
